MJSLAAM: Designing a Sound, Configurable, Efficient, and Pushdown Monadic Static~Analyzer for JavaScript

### 2014-12-13 cs252r-fa14-writeup/paper.tex
writing

@@

\js{} has a large, complex specification and many implementations which
practically define the expected semantics of \js{}. Rather than describe and
implement our own semantics, we implement the \lambdajs{} semantics as described
in \cite{lambdajs}. Additionally, we reused their desugaring program.

We reformulated the \lambdajs{} semantics into a state machine with explicit
continuations. The \lambdajs{} evaluation contexts became our \emph{Frame} data
type. Additionally, we do not divide the evaluation contexts into two sets and
use syntactic stepping rules to implement exceptional control flow. We choose to
implement exceptional control flow with meta functions that crawl the stack
looking for appropriate return points.

@@

@@

The \maam{} framework separates the semantics of a programming language from the
control flow. This same implementation of \lambdajs{} can be used with different
monads to produce path and flow sensitive analysis, as well as other kinds of
analysis. With an appropriate set of monads, traditional points-to constraints
could be generated.

>>>>

The AAM-inspired design process for our final concrete interpreter is
summarized in Figure 1.

@@

\js{} has a large, complex specification and many implementations which
practically define the expected semantics of \js{}. Rather than describe and
implement our own semantics, we implement the \lambdajs{} semantics as described
by Guha et. al. \cite{lambdajs}. Additionally, we reused their Haksell library
as our desugaring front-end.

@@

We reformulated the \lambdajs{} reduction semantics into a state machine
semantics with explicit continuations. The \lambdajs{} evaluation contexts
became our \emph{Frame} data type. Additionally, we do not divide the
evaluation contexts into two sets and use syntactic stepping rules to implement
exceptional control flow. We choose to implement exceptional control flow with
meta functions that crawl the stack looking for appropriate return points.

@@

The \maam{} framework separates the semantics of a programming language from the
control flow. This same implementation of \lambdajs{} can be used with different
monads to produce path and flow sensitive analysis, as well as other kinds of
analysis. With an appropriate set of monads, traditional points-to constraints
could be generated. We note that we did not in the end implement each of these
analyses for \js{}, although we plan to do so in our continuation of this work.
